---
title: "Fabric of Repair Analyses [Public]"
author: 
  - name: "Justin W. Morgan"
    affiliation:
      name: BLIS Collective
      url:  https://www.bliscollective.org/
  - name: "Christina Pao"
date: "8 January 2026"
editor: visual
---

```{r}
#| label: setup code
#| include: false

# Importing Packages
library(tidyverse)
library(magrittr)
library(gtsummary)
library(gt)
#library(ggeffects)
#library(broom)
#library(dotwhisker)
#library(forcats)
#library(stargazer)
#library(showtext)
#library(kableExtra)

#BLIS Color Palette
sunset <- "#F94B01"
cornsilk <- "#F4C900"
jade <- "#1DA595"
petal <- "#F70366"
chestnut <- "#4C230A"
sandstone <- "#F8F2DC" 

# Importing Data
df <- read_csv("Fabric of Repair/data/replication_swayable_2025.csv")
```

## Creating the Analytic Variables

```{r}
#| label: dataset construction
#| message: False

df_analysis <- df %>%
  mutate(Race = race,
         `College Educated` = education_binary,
         Income = factor(case_when(What.is.the.total.annual.income.of.your.household.before.taxes. == "100-150-k" ~ "$100-150K",
                                   What.is.the.total.annual.income.of.your.household.before.taxes. == "under-20-k" ~ "Under $20K",
                                   What.is.the.total.annual.income.of.your.household.before.taxes. == "20-40-k" |
                                     What.is.the.total.annual.income.of.your.household.before.taxes. == "40-60k" ~ "$20-60K",
                                   What.is.the.total.annual.income.of.your.household.before.taxes. == "60-80-k" |
                                     What.is.the.total.annual.income.of.your.household.before.taxes. == "80-100-k" ~ "$60-100K",
                                   What.is.the.total.annual.income.of.your.household.before.taxes. == "150-200-k" |
                                     What.is.the.total.annual.income.of.your.household.before.taxes. == "over-200-k" ~ "Over $150K",
                                   TRUE ~ NA), 
                         levels = c("Under $20K", "$20-60K", "$60-100K", "$100-150K", "Over $150K")),
         `Party Affiliation` = case_when(Party == "democrat" ~ "Democrat",
                                         Party == "republican" ~ "Republican",
                                         TRUE ~ "Independent or Something Else"),
         Residence = factor(case_when(Area == "city" ~ "City",
                                      Area == "in-a-rural-area" ~ "Rural",
                                      Area == "small-town-next-to-native-community-e-g-reservation" |
                                        Area == "small-town-not-next-to-native-community-e-g-reservation" ~ "Small Town",
                                      TRUE ~ "Another location"),
                            levels = c("City", "Small Town", "Rural", "Another Location")),
         Region = case_when(Region..Midwest == T ~ "Midwest",
                            Region..Northeast == T ~ "Northeast",
                            Region..South == T ~ "South",
                            Region..West == T ~ "West"),
         Religion = factor(case_when(What.is.your.present.religion..if.any. == "atheist" ~ "Atheist",
                                             What.is.your.present.religion..if.any. == "catholic" ~ "Catholic",
                                             What.is.your.present.religion..if.any. == "evangelical-protestant" ~ "Evangelical Protestant",
                                             What.is.your.present.religion..if.any. == "mormon" ~ "Mormon",
                                             What.is.your.present.religion..if.any. == "muslim" ~ "Muslim",
                                             What.is.your.present.religion..if.any. == "other-protestant" ~ "Other Protestant",
                                             What.is.your.present.religion..if.any. == "nothing-in-particular" ~ "Not Religious",
                                             TRUE ~ "Other Religion"),
                           levels = c("Not Religious", "Atheist", "Catholic", "Evangelical Protestant", "Other Protestant", "Muslim",  "Other Religion")),
         `Religious Affiliation` = ifelse(Religion == "Not Religious", "Not Religious", "Religious"),
         Enrollment = enrollment_status,
         `Hawaiian Homes Beneficiary` = case_when(Are.you.a.beneficiary.of.the.Hawaiian.Homes.Commission.Act.of.1920..as.amended. == "yes" ~ "Yes",
                                                  Are.you.a.beneficiary.of.the.Hawaiian.Homes.Commission.Act.of.1920..as.amended. == "no" ~ "No",
                                                  Are.you.a.beneficiary.of.the.Hawaiian.Homes.Commission.Act.of.1920..as.amended. == "unsure" ~ "Unsure",
                                                  TRUE ~ NA),
         Residence = case_when(Area == "alaska-native-village" ~ "Alaska Native Village",
                               Area == "city" ~ "City",
                               Area == "hawaiian-homestead-through-department-of-hawaiian-home-lands" ~ "Hawaiian Homestead",
                               Area == "in-a-rural-area" ~ "Rural",
                               Area == "otsa-oklahoma-tribal-statistical-area" ~ "Oklahoma Tribal Statistical Area",
                               Area == "pueblo" ~ "Pueblo",
                               Area == "rancheria" ~ "Rancheria",
                               Area == "small-town-next-to-native-community-e-g-reservation" ~ "Small Town By Native Community",
                               Area == "small-town-not-next-to-native-community-e-g-reservation" ~ "Small Town Not By Native Community",
                               Area == "tribal-reservation" ~ "Tribal Reservation"),
         `Provided Tribal Affiliation` = tribal.affiliation.reported,
         Identity = case_when(Ethnicity..Alaska.Native == T & Ethnicity..American.Indian.Native.American == F & Ethnicity..First.Nations..Inuit.or.Metis == F & Ethnicity..Native.Hawaiian.Kanaka.Maoli == F & Ethnicity..Another.Native..ethnic..or.racial.group.not.identified.here == F ~ "Alaska Native",
                              Ethnicity..American.Indian.Native.American == T & Ethnicity..Alaska.Native == F & Ethnicity..First.Nations..Inuit.or.Metis == F & Ethnicity..Native.Hawaiian.Kanaka.Maoli == F & Ethnicity..Another.Native..ethnic..or.racial.group.not.identified.here == F  ~ "American Indian, Native American",
                              Ethnicity..First.Nations..Inuit.or.Metis == T & Ethnicity..American.Indian.Native.American == F & Ethnicity..Alaska.Native == F & Ethnicity..Native.Hawaiian.Kanaka.Maoli == F & Ethnicity..Another.Native..ethnic..or.racial.group.not.identified.here == F ~ "First Nations, Inuit, Metis",
                              Ethnicity..Native.Hawaiian.Kanaka.Maoli == T & Ethnicity..First.Nations..Inuit.or.Metis == F & Ethnicity..American.Indian.Native.American == F & Ethnicity..Alaska.Native == F & Ethnicity..Another.Native..ethnic..or.racial.group.not.identified.here == F ~ "Native Hawaiian, Kanaka Maoli",
                              TRUE ~ "Other or Multiple Indigenous Identities")) %>%
  select(Age, Gender, Race, `College Educated`, Income, `Party Affiliation`, Residence, Region, `Religious Affiliation`, 
         Identity, Enrollment, Residence, `Provided Tribal Affiliation`, `Hawaiian Homes Beneficiary`, summarized_party, 
         rep_baseline_categorical, landback_baseline_categorical, age_groups, Land.Back.Support, treatment, 
         video_perception, Reparations.Support, Feasibility.Land.Back, Feasibility.Reparations)

df_analysis
```

# Tables

## Table 1. Demographic Distribution of Study Population
```{r}
#| label: table1
#| class: output
#| cache: true

# Creating the descriptives table using gt_summary package
table1 <- df_analysis %>% 
  select(Race, Age, Gender, `College Educated`, Income, `Party Affiliation`, Residence, Region, `Religious Affiliation`) %>% 
  tbl_summary(
    by =  Race,
    percent = "column",
    statistic = all_continuous() ~ "{mean} ({sd})",
    digits = list(all_continuous() ~ 1,
                  all_categorical() ~ c(0, 1)),
    missing = "no") %>% 
  add_overall(last = TRUE) %>% 
  add_p(test = list(everything() ~ "chisq.test",
                      all_continuous() ~ "t.test",
                      Residence ~ "fisher.test"),
          test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE, B = 2000),
          pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  as_gt() %>% 
  opt_table_font(font = "Jost") 

table1
```
## Table 2. Demographic Distribution of Indigenous Study Population
```{r}
#| label: table2
#| class: output
#| cache: true

# Creating the descriptives table using gt_summary package
table2 <- df_analysis %>% 
  filter(Race == "Indigenous") %>%
  select(Identity, Enrollment, Residence, `Provided Tribal Affiliation`, `Hawaiian Homes Beneficiary`) %>% 
  tbl_summary(
    by =  Identity,
    percent = "column",
    digits = all_categorical() ~ c(0, 1),
    missing = "no") %>% 
  add_overall(last = TRUE) %>% 
  add_p(test = everything() ~ "fisher.test",
        test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE, B = 2000),
        pvalue_fun = ~style_pvalue(., digits = 3)) %>%
  as_gt() %>% 
  opt_table_font(font = "Jost") 

table2
```
## Table 3. Support for Reparations and Land Back Movements by Race and Political Affiliation
### Support for Land Back
```{r}
#| label: table3a
df_analysis %>%
  select(Race, summarized_party, landback_baseline_categorical) %>% 
  mutate(`Identity Group` = Race,
         `Political Affiliation` = summarized_party) %>% 
  group_by(`Identity Group`, `Political Affiliation`) %>% 
  count(landback_baseline_categorical) %>%
  mutate(`Sample Size` = n,
         `Support (%)` = round(n/sum(n) * 100, 1)) %>% 
  filter(landback_baseline_categorical == "Support") %>% 
  select(`Identity Group`,`Political Affiliation`,`Sample Size`,`Support (%)`)
```
### Support for Reparations
```{r}
#| label: table3b
df_analysis %>%
  select(Race, summarized_party, rep_baseline_categorical) %>% 
  mutate(`Identity Group` = Race,
         `Political Affiliation` = summarized_party) %>% 
  group_by(`Identity Group`, `Political Affiliation`) %>% 
  count(rep_baseline_categorical) %>%
  mutate(`Sample Size` = n,
         `Support (%)` = round(n/sum(n) * 100, 1)) %>% 
  filter(rep_baseline_categorical == "Support") %>% 
  select(`Identity Group`,`Political Affiliation`,`Sample Size`,`Support (%)`) 
```
  
# Figures
## Figure 1. Baseline Support for Reparations and Landback by Race
```{r}
#| label: figure1
#| fig-column: screen-inset-right
#| cache: true

# Create summary dataframe for Reparations baseline
df_rep_support <- df_analysis %>% 
  group_by(Race) %>% 
  count(rep_baseline_categorical) %>% 
  mutate(Percentage = n/sum(n) * 100) %>% 
  rename(baseline_support = rep_baseline_categorical) %>% 
  add_column(Movement = "Reparations")

# Create summary dataframe for Land Back baseline
df_lb_support <- df_analysis %>% 
  group_by(Race) %>% 
  count(landback_baseline_categorical) %>% 
  mutate(Percentage = n/sum(n) * 100) %>% 
  rename(baseline_support = landback_baseline_categorical) %>% 
  add_column(Movement = "Land Back")

# Merge summary dataframes for Reparations and Land Back
df_support <- bind_rows(df_rep_support, df_lb_support)

# Plot Figure 1
figure1 <- df_support %>% 
  mutate(Race = case_when(Race == "Black" ~ "Black Respondents",
                          Race == "Indigenous" ~ "Native Respondents"))  %>%
  ggplot(aes(x = baseline_support, y = Percentage, fill = Movement)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Baseline Support",
       y = "Percentage",
       fill = "Movement") +  
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  scale_fill_manual(values = c("#1DA595", "#F94B01")) + 
  facet_wrap(~Race) + 
  theme(text = element_text(family = "Jost"),
        plot.background = element_rect(fill = "#F8F2DC"),
        legend.background	= element_rect(fill = "#F8F2DC"),
        legend.position = "bottom",
        legend.title.position = "top",
        panel.background = element_rect(fill = "#F8F2DC"),
        panel.grid = element_line(colour = "#F8F2DC"),
        plot.title = element_text(hjust = 0.5)) 

figure1
```
## Figure 2. Baseline Support for Reparations and Landback by Race and Political Party
```{r}
#| label: figure2
#| fig-column: screen-inset-right
#| cache: true

# Creating a summary dataframe of baseline Reparations support by political party
df_rep_support_pol <- df_analysis %>% 
  group_by(Race, summarized_party) %>% 
  count(rep_baseline_categorical) %>% 
  mutate(Percentage = n/sum(n) * 100) %>% 
  rename(baseline_support = rep_baseline_categorical) %>% 
  add_column(Movement = "Reparations")

# Creating a summary dataframe of baseline Land Back support by political party
df_lb_support_pol <- df_analysis %>% 
  group_by(Race, summarized_party) %>% 
  count(landback_baseline_categorical) %>% 
  mutate(Percentage = n/sum(n) * 100) %>% 
  rename(baseline_support = landback_baseline_categorical) %>% 
  add_column(Movement = "Land Back")

# Combining both Reparations and Land Back dataframes
df_support_pol <- bind_rows(df_rep_support_pol, df_lb_support_pol)

# Plotting Figure 2
figure2 <- df_support_pol %>% 
  ggplot(aes(x = summarized_party, y = Percentage, fill = baseline_support)) +
  geom_bar(stat = "identity") +
  labs(x = "Partisanship",
       y = "Percentage",
       fill = "Support") +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  facet_grid(vars(Movement), vars(Race)) + 
  theme(axis.text.x = element_text(angle = 0)) +
  scale_fill_manual(values = c('#F4C900', '#F94B01', '#1DA595')) + 
  theme(text = element_text(family = "Jost"),
        plot.background = element_rect(fill = "#F8F2DC"),
        legend.background	= element_rect(fill = "#F8F2DC"),
        legend.position = "bottom",
        legend.title.position = "top",
        panel.background = element_rect(fill = "#F8F2DC"),
        panel.grid = element_line(colour = "#F8F2DC"),
        plot.title = element_text(hjust = 0.5)) 

figure2
```
## Figure 3. Baseline Support for Reparations and Landback by Race and Age
```{r}
#| label: figure3
#| fig-column: screen-inset-right
#| cache: true

# Creating a summary dataframe of baseline Reparations support by age groups
df_rep_support_age <- df_analysis %>% 
  group_by(Race, age_groups) %>% 
  count(rep_baseline_categorical) %>% 
  mutate(Percentage = n/sum(n) * 100) %>% 
  rename(baseline_support = rep_baseline_categorical) %>% 
  add_column(Movement = "Reparations")

# Creating a summary dataframe of baseline Land Back support by age
df_lb_support_age <- df_analysis %>% 
  group_by(Race, age_groups) %>% 
  count(landback_baseline_categorical) %>% 
  mutate(Percentage = n/sum(n) * 100) %>% 
  rename(baseline_support = landback_baseline_categorical) %>% 
  add_column(Movement = "Land Back")

# Combining both Reparations and Land Back dataframes
df_support_age <- bind_rows(df_rep_support_age, df_lb_support_age)

# Plotting Figure 3
figure3 <- df_support_age %>% 
  ggplot(aes(x = age_groups, y = Percentage, fill = baseline_support)) +
  geom_bar(stat = "identity") +
  labs(x = "Age",
       y = "Percentage",
       fill = "Support") +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  facet_grid(vars(Movement), vars(Race)) + 
  theme(axis.text.x = element_text(angle = 0)) +
  scale_fill_manual(values = c('#F4C900', '#F94B01', '#1DA595')) + 
  theme(text = element_text(family = "Jost"),
        plot.background = element_rect(fill = "#F8F2DC"),
        legend.background	= element_rect(fill = "#F8F2DC"),
        legend.position = "bottom",
        legend.title.position = "top",
        panel.background = element_rect(fill = "#F8F2DC"),
        panel.grid = element_line(colour = "#F8F2DC"),
        plot.title = element_text(hjust = 0.5)) 

figure3
```
## Figure 4. Persuasion Effects of Garrison's Videos
### Referenced Against Control Video
```{r}
#| label: figure4
#| fig-column: screen-inset-right
#| cache: true

# Regression model for Land Back support
df_model0_lb <- tidy(lm(Land.Back.Support ~ treatment + video_perception, df)) %>% 
  mutate(model = "Land Back Support")

# Regression model for Reparations support
df_model0_rep <- tidy(lm(Reparations.Support ~ treatment + video_perception, df)) %>% 
  mutate(model = "Reparations Support")

# Binding regression coefficient dataframes together
df_model0 <- bind_rows(df_model0_lb, df_model0_rep) %>%
  mutate(conf.low = estimate - 1.96 * std.error,
         conf.high = estimate + 1.96 * std.error) %>% 
  relabel_predictors(c("treatmentReparations" = "Reparations Video",
                       "treatmentLand Back" = "Land Back Video",
                       "treatmentBoth" = "Both Video")) %>%
  filter(!term %in% c("video_perception","(Intercept)"))

figure4 <- df_model0 %>% 
  ggplot(aes(x = estimate, y = term, colour = model)) +
  geom_vline(xintercept = 0, color = "#4C230A", linetype = "longdash", alpha = 0.5) +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high),
                  position = position_dodge(width = 0.5),
                  size = 0.25,
                  linewidth = 0.5) +
  theme(text = element_text(family = "Jost"),
        plot.background = element_rect(fill = "#F8F2DC"),
        legend.background	= element_rect(fill = "#F8F2DC"),
        legend.title.position = "top",
        legend.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "#F8F2DC"),
        panel.grid = element_line(colour = "#F8F2DC"),
        plot.title.position = "plot",
        plot.caption.position = "plot",
        plot.caption = element_text(hjust = 1)) +
  labs(x = " \nCoefficient Estimate with 95% CIs \n",
       y = "",
       caption = "Note: Model includes a control for respondents' perceived production quality.",
       colour = "Model") +
  scale_colour_manual(values = c("#1DA595", "#F94B01"))

figure4
```
##Figure 5. Persuasion Effects of Garrison's Videos by Race
### Movement Support Among Black & Indigenous Audiences 
```{r}
#| label: figure5
#| fig-column: screen-inset-right
#| cache: true
#| message: false
#| warning: false


# Regression model stratified by race for Land Back support
df_model1_lb <-  lm(Land.Back.Support ~ treatment*race + video_perception, df) %>% 
  ggpredict(terms = c("treatment", "race")) %>% 
  tibble() %>% 
  mutate(outcome = "Land Back")

df_model1_rep <- lm(Reparations.Support ~ treatment*race + video_perception, df) %>% 
  ggpredict(terms = c("treatment", "race")) %>% 
  tibble() %>% 
  mutate(outcome = "Reparations")

# Merging predictions
df_model1 <- rbind(df_model1_lb, df_model1_rep)

# Plotting Figure 5
figure5 <- df_model1 %>%
  ggplot(aes(x = x, y = predicted, fill = outcome)) +
  geom_col(position = "dodge") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), 
                position = position_dodge(.9),
                width=.2) +
  labs(x = "Video", 
       y = "Average Support", 
       fill = "Movement", 
       caption = "Note: Model includes a control for respondents' perceived production quality.") +
  facet_wrap(~ group) +
  scale_fill_manual(values = c("#1DA595", "#F94B01")) +
  theme(text = element_text(family = "Jost"),
        plot.background = element_rect(fill = "#F8F2DC"),
        legend.background	= element_rect(fill = "#F8F2DC"),
        legend.title.position = "top",
        legend.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "#F8F2DC"),
        panel.grid = element_line(colour = "#F8F2DC"),
        panel.grid.major.y = element_line(colour = "#4C230A", linetype = "solid", linewidth = 0.1),
        panel.grid.minor.y = element_line(colour = "#4C230A", linetype = "solid", linewidth = 0.1),
        plot.title.position = "plot",
        plot.caption.position = "plot",
        plot.caption = element_text(hjust = 1),
        strip.background = element_rect(fill = "#F8F2DC")) +
  scale_y_continuous(limits = c(0, 10), breaks = c(0, 2.5, 5, 7.5, 10), 
                     labels = c("0, Definitely No", "2.5", "5", "7.5", "10, Definitely Yes"))

figure5
```
##Figure 6. Persuasion Effects of Garrison's Videos by Race and Political Party
### Movement Support Among Black & Indigenous Audiences across  
```{r}
#| label: figure6
#| fig-column: screen-inset-right
#| cache: true
#| message: false
#| warning: false

# Regression model stratified by race and party, Land Back support
df_model2_lb <- lm(Land.Back.Support ~ race*summarized_party*treatment + video_perception, data = df) %>% 
  ggpredict(terms = c("treatment", "race", "summarized_party")) %>%
  tibble() %>% 
  mutate(outcome = "Land Back")

# Regression model stratified by race and party, Reparations support
df_model2_rep <- lm(Reparations.Support ~ race*summarized_party*treatment + video_perception, data = df) %>% 
  ggpredict(terms = c("treatment", "race", "summarized_party")) %>% 
  tibble() %>% 
  mutate(outcome = "Reparations")

# Merging predictions
df_model2 <- rbind(df_model2_lb, df_model2_rep) %>% 
  mutate(x = factor(x, levels = c("Control", "Reparations", "Land Back", "Both")))

# Plotting Figure 6
figure6 <- df_model2 %>%
  ggplot(aes(x = x, y = predicted, fill = group)) + 
  geom_col(position = "dodge") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), 
                position = position_dodge(.9), 
                width=.2) +
  labs(x = "Video", 
       y = "Average Support", 
       fill = "Race", 
       caption = "Note: Model includes a control for respondents' perceived production quality.") +
  facet_grid(vars(outcome),vars(facet)) +
  scale_fill_manual(values = c('Black' = '#4C230A', 'Indigenous' = '#F4C900')) + 
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) + 
  theme(text = element_text(family = "Jost"),
        plot.background = element_rect(fill = "#F8F2DC"),
        legend.background	= element_rect(fill = "#F8F2DC"),
        legend.title.position = "top",
        legend.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "#F8F2DC"),
        panel.grid = element_line(colour = "#F8F2DC"),
        panel.grid.major.y = element_line(colour = "#4C230A", linetype = "solid", linewidth = 0.1),
        panel.grid.minor.y = element_line(colour = "#4C230A", linetype = "solid", linewidth = 0.1),
        plot.title.position = "plot",
        plot.caption.position = "plot",
        plot.caption = element_text(hjust = 1),
        strip.background = element_rect(fill = "#F8F2DC")) +
  scale_y_continuous(limits = c(0, 10), breaks = c(0, 2.5, 5, 7.5, 10), 
                     labels = c("0, Definitely No", "2.5", "5", "7.5", "10, Definitely Yes"))

figure6
```
## Figure 7. Hope Gap for Identity-relevant Movement Among Support
```{r}
########################### Figure 7: Title of Figure ##########################

# Calculating movement support
df_figure7 <- df %>%
  mutate(support_reparations = ifelse(rep_baseline_categorical == "Support", 1, 0),
         support_landback = ifelse(landback_baseline_categorical == "Support", 1, 0),
         feasibility_landback = ifelse(Feasibility.Land.Back == "Yes", 1, 0),
         feasibility_reparations = ifelse(Feasibility.Reparations == "Yes", 1, 0)) %>% 
  filter((race == "Indigenous" & support_landback == 1) | (race == "Black" & support_reparations == 1)) %>%
  mutate(hope = case_when(race == "Indigenous" ~ feasibility_landback,
                          race == "Black" ~ feasibility_reparations)) %>%
  group_by(race) %>%
  count(hope) %>% 
  mutate(Percentage = n/sum(n) * 100) %>%
  mutate(hope = ifelse(hope == 1, "Feasible", "Hope Gap")) %>%
  mutate(movement = "Own Movement",
         hope = factor(hope, levels = c("Hope Gap", "Feasible"))) 
  
# Plotting Figure 7
figure7 <- df_figure7 %>% 
  ggplot(aes(x = race, y = Percentage, fill = hope)) +
  geom_bar(stat = "identity") +
  labs(x = "Identity",
       y = "Percentage",
       fill = "Feasibility") +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  scale_fill_manual(values = c('#F35018', '#1DA595')) + 
  theme(text = element_text(family = "Jost"),
        plot.background = element_rect(fill = "#F8F2DC"),
        legend.background	= element_rect(fill = "#F8F2DC"),
        legend.title.position = "top",
        legend.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "#F8F2DC"),
        panel.grid = element_line(colour = "#F8F2DC"),
        panel.grid.major.y = element_line(colour = "#4C230A", linetype = "solid", linewidth = 0.1),
        panel.grid.minor.y = element_line(colour = "#4C230A", linetype = "solid", linewidth = 0.1),
        plot.title.position = "plot",
        plot.caption.position = "plot",
        plot.caption = element_text(hjust = 1),
        strip.background = element_rect(fill = "#F8F2DC"))

figure7
```

# Code for Study Analysis
In this section we are including code to identify values for statistics produced in our study analysis

Note for Justin - need to update code to View predictions
 
```{r}
#| code-fold: false
#| eval: false

# Viewing Baseline support
df_support

### Calculating predictions by race and video treatment

# Movement regressions
model_landback_race <- lm(Land.Back.Support ~ treatment*race + video_perception, df)
model_reparations_race <- lm(Reparations.Support ~ treatment*race + video_perception, df)

# Movement predictions
predictions_landback_race <- tibble(ggpredict(model_landback_race, terms = c("treatment", "race"))) %>%
  mutate(outcome = "Land Back")
predictions_reparations_race <- tibble(ggpredict(model_reparations_race, terms = c("treatment", "race"))) %>%
  mutate(outcome = "Reparations")

# Merged predictions
predictions_race <- rbind(predictions_landback_race, predictions_reparations_race)

# Black support for reparations with braided video
(predictions_race$predicted[predictions_race$x == "Both" & predictions_race$group == "Black" & predictions_race$outcome == "Reparations"] - predictions_race$predicted[predictions_race$x == "Control" & predictions_race$group == "Black" & predictions_race$outcome == "Reparations"]) / predictions_race$predicted[predictions_race$x == "Control" & predictions_race$group == "Black" & predictions_race$outcome == "Reparations"]

# Black support for landback with braided video
(predictions_race$predicted[predictions_race$x == "Both" & predictions_race$group == "Black" & predictions_race$outcome == "Land Back"] - predictions_race$predicted[predictions_race$x == "Control" & predictions_race$group == "Black" & predictions_race$outcome == "Land Back"]) / predictions_race$predicted[predictions_race$x == "Control" & predictions_race$group == "Black" & predictions_race$outcome == "Land Back"]

# Native support for reparations with braided video
(predictions_race$predicted[predictions_race$x == "Both" & predictions_race$group == "Indigenous" & predictions_race$outcome == "Reparations"] - predictions_race$predicted[predictions_race$x == "Control" & predictions_race$group == "Indigenous" & predictions_race$outcome == "Reparations"]) / predictions_race$predicted[predictions_race$x == "Control" & predictions_race$group == "Indigenous" & predictions_race$outcome == "Reparations"]

# Native support for landback with braided video
(predictions_race$predicted[predictions_race$x == "Both" & predictions_race$group == "Indigenous" & predictions_race$outcome == "Land Back"] - predictions_race$predicted[predictions_race$x == "Control" & predictions_race$group == "Indigenous" & predictions_race$outcome == "Land Back"]) / predictions_race$predicted[predictions_race$x == "Control" & predictions_race$group == "Indigenous" & predictions_race$outcome == "Land Back"]

# Black support for landback increase with reparations video
(predictions_race$predicted[predictions_race$x == "Reparations" & predictions_race$group == "Black" & predictions_race$outcome == "Land Back"] - predictions_race$predicted[predictions_race$x == "Control" & predictions_race$group == "Black" & predictions_race$outcome == "Land Back"]) / predictions_race$predicted[predictions_race$x == "Control" & predictions_race$group == "Black" & predictions_race$outcome == "Land Back"]

# Native support for reparations increase with landback video
(predictions_race$predicted[predictions_race$x == "Land Back" & predictions_race$group == "Indigenous" & predictions_race$outcome == "Reparations"] - predictions_race$predicted[predictions_race$x == "Control" & predictions_race$group == "Indigenous" & predictions_race$outcome == "Reparations"]) / predictions_race$predicted[predictions_race$x == "Control" & predictions_race$group == "Indigenous" & predictions_race$outcome == "Reparations"]

### Calculating predictions by race, partisanship, and video treatment

# Movement regressions
model_landback_raceparty <- lm(Land.Back.Support ~ race*summarized_party*treatment + video_perception, data = df) 
model_reparations_raceparty <- lm(Reparations.Support ~ race*summarized_party*treatment + video_perception, data = df)

# Movement predictions
predictions_landback_raceparty <- tibble(ggpredict(model_landback_raceparty, terms = c("treatment", "race", "summarized_party"))) %>%
  mutate(outcome = "Land Back")
predictions_reparations_raceparty <- tibble(ggpredict(model_reparations_raceparty, terms = c("treatment", "race", "summarized_party"))) %>%
  mutate(outcome = "Reparations")

# Merged predictions
predictions_raceparty <- rbind(predictions_landback_raceparty, predictions_reparations_raceparty)

# Native Democrats' support for landback with braided video
(predictions_raceparty$predicted[predictions_raceparty$x == "Both" & predictions_raceparty$group == "Indigenous" & predictions_raceparty$facet == "Democrat" & predictions_raceparty$outcome == "Land Back"] - predictions_raceparty$predicted[predictions_raceparty$x == "Control" & predictions_raceparty$group == "Indigenous" & predictions_raceparty$facet == "Democrat" & predictions_raceparty$outcome == "Land Back"]) / predictions_raceparty$predicted[predictions_raceparty$x == "Control" & predictions_raceparty$group == "Indigenous" & predictions_raceparty$facet == "Democrat" & predictions_raceparty$outcome == "Land Back"]

# Native Democrats' support for reparations increase with landback video
(predictions_raceparty$predicted[predictions_raceparty$x == "Both" & predictions_raceparty$group == "Indigenous" & predictions_raceparty$facet == "Democrat" & predictions_raceparty$outcome == "Reparations"] - predictions_raceparty$predicted[predictions_raceparty$x == "Control" & predictions_raceparty$group == "Indigenous" & predictions_raceparty$facet == "Democrat" & predictions_raceparty$outcome == "Reparations"]) / predictions_raceparty$predicted[predictions_raceparty$x == "Control" & predictions_raceparty$group == "Indigenous" & predictions_raceparty$facet == "Democrat" & predictions_raceparty$outcome == "Reparations"]

# Native Republicans' support for reparations increase with landback video
(predictions_raceparty$predicted[predictions_raceparty$x == "Land Back" & predictions_raceparty$group == "Indigenous" & predictions_raceparty$facet == "Republican" & predictions_raceparty$outcome == "Reparations"] - predictions_raceparty$predicted[predictions_raceparty$x == "Control" & predictions_raceparty$group == "Indigenous" & predictions_raceparty$facet == "Republican" & predictions_raceparty$outcome == "Reparations"]) / predictions_raceparty$predicted[predictions_raceparty$x == "Control" & predictions_raceparty$group == "Indigenous" & predictions_raceparty$facet == "Republican" & predictions_raceparty$outcome == "Reparations"]

# Black Democrats' support for Land Back increase with Reparations video
(predictions_raceparty$predicted[predictions_raceparty$x == "Reparations" & predictions_raceparty$group == "Black" & predictions_raceparty$facet == "Democrat" & predictions_raceparty$outcome == "Land Back"] - predictions_raceparty$predicted[predictions_raceparty$x == "Control" & predictions_raceparty$group == "Black" & predictions_raceparty$facet == "Democrat" & predictions_raceparty$outcome == "Land Back"]) / predictions_raceparty$predicted[predictions_raceparty$x == "Control" & predictions_raceparty$group == "Black" & predictions_raceparty$facet == "Democrat" & predictions_raceparty$outcome == "Land Back"]

# Black Democrats' support for Reparations increase with Braided video
(predictions_raceparty$predicted[predictions_raceparty$x == "Both" & predictions_raceparty$group == "Black" & predictions_raceparty$facet == "Democrat" & predictions_raceparty$outcome == "Reparations"] - predictions_raceparty$predicted[predictions_raceparty$x == "Control" & predictions_raceparty$group == "Black" & predictions_raceparty$facet == "Democrat" & predictions_raceparty$outcome == "Reparations"]) / predictions_raceparty$predicted[predictions_raceparty$x == "Control" & predictions_raceparty$group == "Black" & predictions_raceparty$facet == "Democrat" & predictions_raceparty$outcome == "Reparations"]

# Black Democrats' support for Land Back with Braided
(predictions_raceparty$predicted[predictions_raceparty$x == "Both" & predictions_raceparty$group == "Black" & predictions_raceparty$facet == "Democrat" & predictions_raceparty$outcome == "Land Back"] - predictions_raceparty$predicted[predictions_raceparty$x == "Control" & predictions_raceparty$group == "Black" & predictions_raceparty$facet == "Democrat" & predictions_raceparty$outcome == "Land Back"]) / predictions_raceparty$predicted[predictions_raceparty$x == "Control" & predictions_raceparty$group == "Black" & predictions_raceparty$facet == "Democrat" & predictions_raceparty$outcome == "Land Back"]

# Indigenous Democrats' support for Reparations with Braided
(predictions_raceparty$predicted[predictions_raceparty$x == "Both" & predictions_raceparty$group == "Indigenous" & predictions_raceparty$facet == "Democrat" & predictions_raceparty$outcome == "Reparations"] - predictions_raceparty$predicted[predictions_raceparty$x == "Control" & predictions_raceparty$group == "Indigenous" & predictions_raceparty$facet == "Democrat" & predictions_raceparty$outcome == "Reparations"]) / predictions_raceparty$predicted[predictions_raceparty$x == "Control" & predictions_raceparty$group == "Indigenous" & predictions_raceparty$facet == "Democrat" & predictions_raceparty$outcome == "Reparations"]

# Indigenous Republicans' support for Reparations with Reparations
(predictions_raceparty$predicted[predictions_raceparty$x == "Reparations" & predictions_raceparty$group == "Indigenous" & predictions_raceparty$facet == "Republican" & predictions_raceparty$outcome == "Reparations"] - predictions_raceparty$predicted[predictions_raceparty$x == "Control" & predictions_raceparty$group == "Indigenous" & predictions_raceparty$facet == "Republican" & predictions_raceparty$outcome == "Reparations"]) / predictions_raceparty$predicted[predictions_raceparty$x == "Control" & predictions_raceparty$group == "Indigenous" & predictions_raceparty$facet == "Republican" & predictions_raceparty$outcome == "Reparations"]
```
